\documentclass{article}
\usepackage{filecontents}
\usepackage[authoryear]{natbib}
\usepackage{usebib}

\begin{document}
\title{GEOG701 Annotated Bibliography}
\author{Dylan Skrah}
\maketitle
 
\begin{enumerate}

\item \cite{monarrez2021RaciallyUnequal}
  
This paper evaluates ethnic and racial compositions of neighboring
schools to find discontinuities. The question is to what extent do
neighboring schools segregate their populations and school resources
(such as staffing). The authors find over 2000 pairs of neighborhoring
schools that are vastly different from each other in ethnic
composition and resources, suggesting that school attendance
boundaries (SABs) are drawn in ways that amplify segregation,
intentionally or otherwise. They link existing inequalities to those
created by the New Deal's Home Owners' Loan Corporation redlining
policies using historical maps. While they use SABs extensively, they
source their data privately, rather than using the public School
Attendance Boundary Survey.


\item \cite{saporito2016IrregularlyShaped}

This paper contextualizes the 'school attendance zone' or 'school
attendance boundary' (SAB) as a concept in education research and
demography. The authors establish the benefits of diverse schools and
argue that the drawing of SABS is one of the best tools available to
administrators to increase diversity. They explore the causation and wv
directionality of segregation in neighborhoods in schools, considering
the 'regularity' of school catchment zones, meaning if the zone is
square/rectangular/compact or irregular/large/amorphously drawn, and
show that the more irregularly drawn (i.e. not rectangular) shapes
contribute to school diversity. Compact, rectangular SABs tend to
mirror the demographic makeup of the overall city, meaning that a grid
of SABs will simply reproduce the existing segregation in the
city. SABs which are 'gerrymandered' to be sprawling and irregular can
draw students from across different ethnic neighborhoods in the city,
resulting in a more diverse school. The thesis of this paper is that
segregation in schools is largely driven by segregation patterns in
the local residential areas, though this not a universally agreed upon
pathway.They develop measures of irregularity, including concavity,
convex hulls, and Polsby-Popper. As well, they calculate spatial
clustering and absolute diversity measures for race/ethnicity. Shape
comparisons are made to US congressional districts and find that on
average, school catchments are mostly regular, but that some are very
irregular. The major finding of this paper is that the irregularly
shaped catchments are almost always more diverse than the compact
catchments.They use the 2009 SABINS database to show that this pattern
largely holds, that irregularly drawn SABs almost always have diverse
schools.



\item \cite{rey2011MeasuringSpatial}
  
This paper is concerned with advancing the study of spatial dynamics
of neighborhoods, as opposed to neighborhood composition; i.e. spatial
boundaries of a neighborhood vs. the people that live within it. The
authors argue that while both are critical for understanding
neighborhood change, the study of spatial boundaries is vastly
underinterrogated compared to neighborhood composition. The framework
presented ivolves regionalizing census tracts (using a Max-P
algorithm) in Metropolitan Statistical Areas for two time periods and
then investigating 22 neighborhood characteristic variables from
census. Results were examined in the regionalized study area
(neighborhoods) and at the /a priori/ level (tracts). The findings
suggest that higher density, smaller land area, and more centrally
located (centrality) neighborhoods tend to experience the highest
degree of change.


\item \cite{fu2020PromotingGeography}

This article asks Q1: Which disciplines are most quantitively interact
with geography for the purpose of advancing sustainability science;
Q2: How to best promote geograpic sciences in transdisciplinary
methodologies /public policly/, /urban planninging/. The author
collect data on frequencies of 11 words that appear with "geography" +
"sustainability" in titles, keywords, and abstracts in publications of
the ISI Web of Science from 2010 to 2019. The resulting associations
between geography, sustainability are orgazied along different
dimmensions, such as research objects, policy areas, and modelling
methodology. The author then theorizea and describes 5 distinct
spheres of research that geographers could pursue to advance the use
of geographical methods into sustainability studies: Geographical
processes, Ecosystem services and human wellbeing, Human-Environmental
Systems, Sustainable development, and Geo-data and models for
sustainability.


\item \cite{thatcher2016DataColonialism}

This article contributes to theoretical understanding of the role of
big data in capitalist production. Through End User License Agreements
and myrriad smart devices and sensors, technology firms collect and
aggregate data in a way that resembles David Harvey's Accumulation by
Dispossession. Individual data points are abstracted away from the
"lifeworld" and algorithmicly processed to generalize and predict
purchasing and consumption patterns. "Social norms, aesthetic
pleasures, and perceived values encourage the use of an increasing
array of technologies equipped with sensors that quantify and then
communicate data about previously private times and places to
third-party actors." This process is termed "data colonialism," to
contrast with the framing of technological advancements as "digital
frontierism." Further investigation in this area for me is the role of
big data in the "filtering" of news and personal information feeds
from the basis of the aggregated digital identities created by
dispossed data.


\item \cite{crampton2015CollectIt}

This paper provides a study of the complications of the techonological
advancement of big data. It draws primarily from examples of
consequences drawn from the US Intelligence Agencies (IC) and are
primarily divided into two categories: (geo)privacy and algorithmic
security. "Big data are a matter of technologic /practices,
epistimologies, and ontologies/." The article provides a detailed
summary of key facts about the IC revealed by the Snowden documents;
personel, budgets, specific operation details, and entertains the
legal arguments surrounding things like bulk surveillance and
'incidental collection'. The author argues that corporate activities
actively extend the state by increasing its reliance on the private
sector; government purchases data, underwrites research, funds
operations that increase government's depth of view. The paper touches
on uses of big data by the government for warfare, particularly with
drones in the war on terrorism. The author provides avenues for future
research: Better histories of development of geospatial IC, better
accounting for IC operations, better encryption and legal protections
(informed consent about government surveillance.


\item \cite{laniyonu2018CoffeeShops}

This article presents an empirical analysis of the post-industrial
policing hypothesis by operationalizing gentrification and applying
spatial Durban models in New York City between 2010 and 2014. Spatial
Durbin models an outcome of interest as a function of endogenous
interaction effects, direct effects, and exogenous interaction
effects. Effects are modelled based on differing theories to explain
the spatial variation of policing, including rational-beauracratic
theory, and conflict theory; racial threat, economic threat. Initial
analysis yields support for all of these theories - Effectively, the
Durbin modelling reveals that gentrification in a given tract is very
strongly associated in increases in policing in neighboring tracts,
but negatively associated in itself. As well, these effects vary with
the extent of gentrifiation that has occurred - the author
distinguishes between tracts inelligable for gentrification, tracts
elligable, and post-gentrified tracts. These findings support the
notion that police are utilized to drive undesired persons from a
given area to make it more ammenible to the in-moving richer, whiter
population. The poorer, darker population is corralled and heavily
policed in adjacent tracts. Police ramp up their postindustrial
policing practices in areas known to be undergoing change
(i.e. experienced influx of 'undesirable' people).


\item \cite{sampson1997NeighborhoodsViolent}

This article is a study of the correlates of violent crime across
varried neighborhood contexts, using the Project on Human Development
in Chicago Neighborhoods dataset; the census tracts of which were
regionalized into neighborhood clusters. The basic hypothesis is that
collective efficacy, and through it informal social control, can
explain the variation of violent crime across neighborhoods. Things
like duration of tenacy and homeownership matter more than economic
stratification or demographic factors (race). The methodology involves
a hierarchical model of variations within persons, variations within
neghborhoods, and variations between neighborhoods to get at
correlates of social cohesion. After operationalizing collective
efficacy, the author finds that collective efficacy is negatively
related to violence in neighborhoods using regression
modelings. Several additional tests were run to determine the extent
that previous homicides, concentrated disadvantage, immigrant
concentration and resident stability factor into violent crime, and
found that collective efficacy was by far the largest effect. The
results imply that collective efficacy can be meausured reliably at
neighborhood scales and is relevant to the story of violent crime in
Chicago neighborhoods. One major flaw of the study is that the
operationalization of collective efficacy is done by collecting survey
responses rather than actually observed.

\item \cite{herring2014NewLogics}
  
This paper demonstrates a good deal of variation in large homeless
encampments, and attempts to develop a typology. The study is the
first to comparitavely examine variegated homelessness within a single
analytical framework, consisting of 12 encampments across 8
municipalities on the west coast. The result is a topology of 4 kinds
of encampments: /co-optation/, /accomodation/, /contestation/, and
/toleration/. The author utlizes interviews with municipal
administrators, non-profit actors, and the homeless residents, as well
as living in the communities from a period fo 2009 to 2011. The
typology reveals that the type of encampment is largely
``co-structured by policies of the state and the adaptive strategies
of homeless people and their allies in their particular urban
context.'' This is clear by contrasting the aesthetics, purpose, and
results of Portland's Dignity Villiage (accomodation) with the
prison-like structure and restrictions of Ontario's THSA
(co-optation). These two examples represent the 'legal' end of the
typology. The illegal encampments range from serving an explicitly
political goal of bringing awareness to homelessness (contested) to
mirroring representations of condensed poverty, including the open-air
drug markets (toleration). This paper should be considered in a
continuum of post-industrial policing in service of
capital. Underlying many of the findings in this paper are the facts
that municipalities take these actions at the behest of landed
residents and commercial interests.

\item \cite{certoma2020DigitalSocial}

This paper is a review of a new concept called Digital Social
Innovation (DSI), which refers to innitiatives that attempt leverage
digital technologies to co-create solutions to a wide variety of
social needs. DSI is associated with the development of``smart
cites.'' The paper argues that a applying a critical geography lens to
these initiatives could yield important perspectives about the power
relationships involved. The author thus elaborates on 4 avenues of
research that critical geographers should pursue. The suggested agenda
starts with investigating DSI as networks of networks and
deconstructing mainstream narratives about smart hyperconnected city
in relation to the reproduction of capitalism. Are cities laboratories
for technocratic governmental solutions? Are they incubators of
citizen critical engagement or do they aid in the production of state
and market power? This article is a little obtuse without any prior
knowledge of some of the works referrenced. Further investigation:
\emph{Manifesto for Digital Social Innovation (Chic 2020), Ind.ie,
Mastodon, Digital Space (concept)}.


\item \cite{andreasson2022ErodingPublic}

This article demonstrates a system dynamics model to model the
influence of the American Legislative Exchange Council (ALEC, the
conservative lobbying group) on American legislative process through
their increased membership. The political science literature guiding
the model suggests that a shift in governance to 'network governance'
is causing a reduction of resources in public institutions via the
creation of new institutions. New problems result in the creation of
new institutions, which absorb resources away from the existing
institutions. The model demonstrates 6 feedback loops that reinforce
and increase ALEC membership and influence in the legislative
process. The authors then employ scenario analysis, wherein several
hypothetical situations (based on 'what if'-ing real events,
i.e. corporate backlash after the Trayvon Martin killing was linked to
ALEC) are evaluated against a baseline scenario. The explanations
provided by the model make sense and are intuitive, but the data
driving the model is mostly implied, and unclear - the specific
driving points are unstated. ALEC is very secretive with its data and
does not generally assist in this expose. I might consider more
research on system dynamics methodology in the event I want to model
political behavior.

\item \cite{richardson2019DirtyData}

This paper expands upon the term 'dirty data' to reflect the nature of
data production in policing - derrived from corrupt and unlawful
practices, and presents three case studies of police departments that
were simulatniously under a consent decree or some other federal
investigation while developing predictive policing systems. The idea
is that these departments are under investigation as a result of their
corrupt practices (including dirty data creation and utilization)
while using those practices to inform their predictive systems. I read
the Chicago section, which describes the Strategic Subject List, which
was both ineffective at its stated goal and entirley informed by the
corrupt and biases practices that preceeded it. The paper ultimately
argues that dirty data exists systemically in the criminal justice
system. The paper concludes with a brief, but concise discussion of
the role of police as servants of capital (my interpretation), the
dynamics of gentrification and the threat/consequences of unabatted
use of dirty data in policing systems.


\item \cite{batty1997VirtualGeography}

This paper is a widely cited typology of new frontiers created by the
intersection of computers and geography. The author delineates and
defines 3 distinct aspects of the digital world that are relevant to
geography: cspace: the space within computers, cyberspace: the use of
computers to communicate, and cyberplace - the infrastructure of the
digital world. The author presents these aspects as interconnected and
constantly influencing each other, along with the traditional concept
of space/place. In this context, it seems that I would be interested
most in cyberplace and the implications of its growth on public
systems - how better systems can help improve society but more
critically safeguarding against the dangers big data imply: the
destruction of any concept of privacy or control over ones own
life. The paper is relatively dated given the advance of technology in
the previous two decades, and there is sure to be more recent works
that I should investigate for any concrete phenomenon which might
overlap with my research interests.

\item \cite {speer2016RightInfrastructure}

This paper describes and advances an argument for the right of the
homeless to a 'right to the city', originally articulated by Lefebver
in 1996 (?); effectively arguing for a more dignified life decoupled
from capitalist commodification of housing and sanitation
infrastructure. The article details the conditions endured by Fresno's
homelessness community using interviews and visits to encampments over
several months. There is a discussion of municipal policy to displace
and dehumanize the homeless while refusing to consider ammeliorating
the conditions on the ground, primarily waste and sanitation
services. A lot of the paper has to do with accesss to bathrooms for
bodily autonomy. Public defication, urination, bathing, love-making,
is dehumanizing, but conditions are such that nobody wants to provide
(pay for) a solution for preventing it, so instead it is mobilized to
advance arguments for destoying encampments. This paper has
heartbreaking accounts of destruction of makeshift homes and treasured
posessions to advance the normative arguments presented.

  
\item \cite{dewitt2022TwistedFate}

This comment is a law review of the California Environmental Quality
Act (CEQA), in which the history of the evoluation of CEQA is
described - the motivation, formulation, passage, and eventual
mobilization and weaponization of the legislation to block
construction projects, particularly as it relates to housing. It also
highlights 3 major ways that California has attempted to circumvent,
weaken the blockade of CEQA, mostly through state legislation: SB540,
AB70, and AB73. These leverage other mechanisms in the state, such as
the Regional Housing Needs Assessment - if the municipality isn't
within projections to meet the needs as defined by the RHNA, certain
CEQA requirements, time constraints, etc. could be bypassed. Because
these bills needed leglislative concesssions to pass, such as
requirements that developers pay workers prevailing wages, or that
they bills fail to pass at all, they are largely inneffective for
increasing the State's housing stock. The author concludes that
solutions from within the stateare not viable, and that California
should consider adopting policy fixes from other states: MA, MN, and
NY, in ways that streamline the regulatory steps involved in housing
development. These mostly involve trying to protect developments from
frivolous or otherwise counterproductive CEQA lawsuits: removing
anonymity, creating municipality-specific CEQA processes, enacting
housing-friendly zoning statutes, and others. Ultimatley these are all
subject to California's Supreme Court and have their own
barriers. CEQA remains a impenetrable barrier for increasing the
supply of housing in the state, seemingly in service of landed Capital
to pursue commercial developments and upscale housing above
multi-family dwellings, apartment buildings, and low income housing.

\item \cite{kauppinen2022UnderstandingEffects}

This article is an empirical investigation of the causes of
segregation in schools in Helsinki, Finland. The study design uses the
total population in the city and school catchment zones to create a
regression discontinuty design to determine if national origin
(operationalized as `Western' vs 'Non-Western' is a causal factor in
residential/neighborhood and school selection and driving
segregation. Several distinctions can be made between school systems
in Helsinki vs. the US, including the extent of privitization and
charter schools that exist here but not there. Catchment boundaries
are found to be a causal factor in intra-urban residental
mobility. The results are stratified by income and household
composition (single person, dual persons, dual persons with child
under 7, dual persons with child over 7, etc. The greatest
pronouncement of the boundaries as a causal factor in migration was
found in high income people with children under school age: wealthy
parents utilize their resources to select what they think are the
better schools, determined by the share of non-western migrants and
subsidized housing in the catchment zone.

\item \cite{bernelius2019PupilsMove}

This paper is an analysis of the two-way relationship between school
catchment segregation and urban residential mobility in Helsinki,
Finland. The city is an interesting case due to the (self-proclaimed)
egalitarian nature of Nordic civic infrastructure - the quality of
schools not only exceed those in the US, but they are largely uniform
across the city in quality and resources. The main finding of this
paper is that despite the uniformity, urban mobility and segregation
can be linked to parent's perceptions of school/neighborhood quality
in the sense of demographic factors. The data demonstrates that while
housing decisions are influenced by multiple factors, the catchment
areas are linked to residential mobility patterns of native Finns in
systematic ways: family mobility is higher when the child is not
school-aged, but drops off dramatically once they are. Parents move to
try to get the 'best' socioeconomic context for their children, and
stop once the childs networks are being established.

\item \cite{burrell2021SocietyAlgorithms}

This article is a thorough reading of literature concerned with 'Big
Data' and discusses the social implications of the various
transformations caused. It takes a particularly marxist perspective by
positing the rise of a new occupational class called the coding elite,
who has consolidated power through technical control and therefore the
digital means of production over the marginalized class: cybertariat
  
\item \cite{florida2003CitiesCreative}

This article is generally exploring dynamics of social ties and social
makeups in regional/city transformation and development. Florida is
refuting claims about the importance of social capital, positing that
in the modern era, people want quasi-anonymity and don't really want
to live in ties that are invasive or prevent them from pursuing their
own lives. He then lays out a theory of the creative class, a cadre of
people that are educated and creative are the primary drivers of
economic growth in cities and regions. The rest of the paper attempts
to quantify three theories, ocial capital, human capital, and creative
class, as being determinitive of the growth of a city. The general
conclusion is that social capital is much less predictive than human
capital, while creative class out-predicts them both. The paper is
generally opaque in that these theories are quantified into indexes
that the reader don't get to read, though the entire paper is
generally an abstraction of his book, which presumably has more
details. The creative class putting a high value on 'tolerance'. All
of the concepts in this paper are not sufficiently defined for me to
judge them on their merits due to this artcile being a summary of
Florida's 2003 book, rise of the creative class.
  
\item \cite{woods2017DevelopmentArrested}

Development Arrested is a seminal work that combines several
methodologies to describe the history of development in the region
known as the Mississippi Delta. The work is largely concerned with the
power structures involved in the creation, action, and dissolution of
administrative bodies in the region; but Woods also draws upon the
development of culture in the region, and as such this book is also an
epistomology of the blues, broadly defined.

Supporting articles: \cite{isenberg2004SymposiumWoods},
\cite{tiefenbacher2019DevelopmentArrested}

\item \cite{golumbia2009CulturalLogic}

The Cultural Logic of Computation presents a critique of the ideology
that David Golumbia calls 'computationalism', which is the belief that
computers and algorithms \emph{can and must} underwrite the
fundamental organization of society and the distribution of
resources. The book begins by placing computationalism in relationship
to the works of Noam Chomsky, who's works have largely redefined the
field of linguistics. Golumbia argues that The implications of Chomsky
lead to computationalism, which is most fulfilled and complete in an
authoritarian state, rather than the leftist ideology that Chomsky
publicly espouses. Eventually, the book moves to discuss
computationalism in the context of global culture and the advancement
of technology, and in particular the notion that computationalism is a
logical extension of rational individualism which itself is often
deployed to support neoliberal economic arrangements. The contrast
between the communitarian ideal that computers are marketed to evoke
and the reality that they are utilized to impose a top-down,
anti-democratic, even authoritarian ideology is a recurring theme in
the book.


\item \cite{brazil2022MeasuringMapping} This article is a comparison
  of 5 different methodologies that can be used to measure opportunity
  (or lack thereof) in neighborhoods. The methods compared are:
  California: CalEnviroScreen 3.0 (CES), Child Opportunity Index 2.0
  (COI), Low Income HousingTax Credit Opportunity Index (LIHTC),
  Opportunity Atlas, and the Regional Opportunity Index (ROI). The
  general disagreement between each of these indexes was more
  substantial in the higher opportunity areas in the state. The major
  take away from this study is that measuring opportunity for policy
  applications should not be performed in a one-size-fits-all capacity
  - instead the measures taken should be carefully considered
  alongside the type of programs that are designed to be
  implemented. As well, low opportunity designations may carry a
  degree of stigma that could negate the programs being implemented,
  and the general disagreement at the high opportunity (lower income)
  end of the mapping suggests that these are sometimes applied more
  arbitrarily than it might seem.

\item \cite{burdick-will2018SchoolLocation} This paper tests two
  hypothesis regarding the `placeness' of elementary schools: first
  that parents of students will report stronger ties to the friends
  and neighbors also attached to that school, and second that parents
  will shift the orientation of their percieved neighborhood
  boundaries in the direction of the school their child attends. These
  are tested using the Making Connections survey, which surveys 28
  low-income schools in 10 cities. Importantly, the survey includes
  questions that require respondants to draw the physical boundary of
  their neighborhoods in relation to the location of the
  school. Results confirm both hypotheses, but the methods used to
  confirm H2 (drawing) are a bit confusing. I should return to this
  paper to evaluate the findings when I have a better understanding
  (and more time!)

  
\item \cite{church1993ModelingSchool} This paper is responding to a
  model formulated by (Diamond and Wright, 1987), who were trying to
  optimize school closures and school utilization. Church and Murray
  show that the Diamond and Wright paper biased the closures of lower
  capacity schools, which would result in utilization problems across
  a district. A major problem with the original formulation is that it
  minimizes the deviation between open and closed schools, which leads
  to the closure of smaller schools, regardless of location, because
  it would lower average utilization rates.This leads to a discussion
  about school utilization rates more based in reality - a school is
  not optimally utilized at 100 percent capacity because the school
  needs to have some operating space for student fluctuation both
  during and in-between academic years.  To adjust, Church and Murray
  add an additional constraint to the model, which accounts for
  deviation between only schools that remain open.The adapted model is
  then turned loose on a hypothetical (toy) dataset of 15 tracts and 5
  schools. I must remember that I was 1-years-old when this paper came
  out so the computing power (which is boasted about in the paper) had
  significantly less capacity than it does now. Though the model is
  saled up to a larger dataset (200 tracts and 9 schools, unclear if
  it is a real area), the use of toy data for the model really
  detracts from its usefulness at this point in time due to the degree
  of assumptions it takes - particularly equallity in capacities and
  racial balances

\item \cite{gubits2018WhatInterventionsa} This paper is an analysis
  about different approaches to addresssing homelessness. It
  specifically wants to understand if long term housing assistance is
  more effective relative to other, less generous policies. The study
  employes over 2000 families across 12 sites and models effectiveness
  between transitional housing, short term housing subsidies, and long
  term housing subsidies. The long term interventions resulted in
  fewer instances of homelessness, food insecurity, and other
  indicators of well-being at a cost that was on average 9 percent
  higher than other interventions. As well, the model indicated that
  the less generous interventions have little effect on these metrics.

\item \cite{healy2017PublicSociology} In his provocatively titled
  ``Fuck Nuance, Kieran Healy describes three kinds of 'nuance traps'
  that are common in sociology, some of which are applicable to my
  work. Most of these have to do with understanding that nuance is not
  a replacement for theory, that having a high resolution model with
  tons of data points is largely useless without a theoretical
  principle to guide hypothesis. Ultimatley, this paper argues for
  more rigorous investigations of theories that guide research in a
  effort to make them more robust. An underrated part of Healy's
  writing is how he describes the role of an academic in the public
  age. In particular he argues that to the extent possible,
  sociologists should participate in public debates and posit their
  theories on social media (he recommends twitter), but cautions the
  various traps that are innevitable in this particpation.

  
\item \cite{herring2019ComplaintOrientedPolicinga} This article
  demonstrates a turn in the orientation of policing towards 'quality
  of life' complaints against the homeless. These complaints stem from
  a massive increase in ``anti-social behavior'' laws across the
  United States (probably as a result of an increase in the homeless
  population. These include bans on camping, sleeping in public,
  loitering, living in vehicles, and more. On average, cities in
  California have 9 anti-homeless laws (LA and SF have 21 and
  24). This article contains a plethora of qualitative work that
  describes the formulation of anti-homelessness policy and reactions
  from municipalities, including the `shuffling' of poverty around the
  city, and the privelidging of high impact areas (such as near where
  city officials live). Its primary data source is a hoard of 311
  calls. See the vignette at the start of the article: ``We're playing
  a massive game of whack-a-mole... I get it, but where are they
  supposed to go?''

\item \cite{leckie2009ComplexitySchool} This UK article explores the
  relationships of pupil mobility to academic acheievment. The author
  argues that even advanced modeling techniques fail to acknowledge
  that various moves during a student's academic career can impact
  achievement. Unsurprisingly, the author finds that moving during
  school is negatively associated with academic performance, though
  the strength of this effect is dependent on the timing of these
  moves. A major finding is that a strong primary school effect
  (finishing the entirety of primary school in one location) has
  positve lasting effects on academic performance. This augments
  rather than contradictions previous findings that secondary schools
  were the more important as the author still finds strong effects.

\item \cite{murray2000SpatialCharacteristics} This paper presents and
  analyzes the differences between two clustering models: the
  Interaction Clustering Problem (ICP) and the Median Clustering
  Problem (MCP). ICP is much more sensitive to the functional quality
  of cluster groupings than is the MCP. That is, when an MCP grouping
  is evaluated as an ICP, it always results in a functional difference
  that is greater than when an ICP grouping is evaluated as an
  MCP.There are large and numerous occurrences of functional
  dissimilarity between evaluated clusters for ICP. The use of the MCP
  to approximate the ICP resulted in clusters which were as much as 46
  percent less efficient - therefore, for [[exploratory spatial data
      analysis]] and GIS applications dealing with interaction more
  generally, The ICP should be preferred.

\item \cite{owens2016IncomeSegregation} This collaboration of
  segregation scholars is an investigation of income segreation
  dynamics in schools and school districts. By combining Census and
  CCD (school) data, they investigate trends of these dynamics through
  . The general finding is that income segregation increased from 1990
  to 2010 by about 17 percent with 28 percent STD. This paper is
  useful for its thorough evaluation of different factors that could
  be independent variables in regression modeling in the
  school-neighborhood nexus, as well as a formulation of Rank Order
  Index (Reardon2011) to model segregation. This is a good one to
  review for a general understanding of the dynamics of school
  segregation since 1990.

\item \cite{takahashi2002SociospatialStigmatization} This paper
  presents an analysis of 8 semistructured interviews with homeless
  women with children in Orange County to determine to what extent
  their status as parents coincides with the stigmitization of
  homelessness as a major barrier to reentery. A takeaway from this
  article is that despite the fact that all participants were employed
  and housed, they reported that their status as homeless was
  constantly reinforced by family, friends, and social workers, in
  ways that resulted in shame, which they cited as reasoning for not
  enrolling in services or benefits that might have aided them. These
  interviews were performed in 1998 however - culture around
  homelessness services and the transitional housing from which the
  respondents were recruited may have shifted.

  
\item \cite{williams1961AdvertisingMagic} This is an essay that was
  origianlly published in Raymond William's 1961 book that I
  originally read in my undergraduate Media and Cultural studies
  program. It is a narrative history of the development of the
  advertising industry that I associate with the family of cultural
  critics; chomksy, adorno and horkheimer, stuart hall, gramsci,
  etc. The rage in the quote from losing yet another public space to
  advertising is reflects the general feeling of dread and
  disappointment that I get from recalling watching the internet
  develop over time. the internet experience grew from the mysterious
  place I used to play browser games and chat with my friends over AIM
  as a kid into this thing that is supposed to represent humanity's`
  salvation but has just become an unnavigable deluge of advertising,
  data farming, third-party-isms and EULAs.
\end{enumerate}


\bibliographystyle{apalike}
\bibliography{701.bib}


\end{document}
